### 2021-03-25 Chapter-2/Chapter-2.tex
Updates from Overleaf

Some other side-channel targets also include spell checking tools, and font libraries~\cite{xu2015controlled}. The attack to font libraries is essentially the same as the attack to the graphic library like GTK. By exploiting the differences of memory accesses when the program renders different characters, an attacker can recover parts of the original sensitive information. Other side-channel attacks target on the kernel of the operating system. We list two examples here. One example is the to use the side-channel attacks to break the kernel address space randomization (KASLR).
Many exploits rely on the knowledge of the memory location of a certain kernel function. Since Linux 4.12, the kernel loads core kernel image and device drivers at random positions during the boot time. Jang et al.~\cite{jang2016breaking} rely on side-channels to reveal mapping status of each page. After that, they detect kernel modules with unique size signatures to break KASLR.

\section{Detection and Mitigation}
While there are several existing work on side-channel leakage detections, we find it very hard to apply existing methods to identify controlled-channel attacks. According to Table~\ref{table:related_work}, existing methods can be classified into two categories, tools based on the trace comparison and tools based on the abstraction.

\textbf{Trace comparison.} If the victim program has two different execution traces with two different sensitive inputs, then we can distinguish the sensitive input by observing the execution trace. Therefore, we can conclude the program is vulnerable to side-channel attacks. The method is similar to UNIX tool \textsf{diff}. Moreover, the approach does not need to model or abstract the program's semantics. In general, the approach is quite salable. On the negative side, comparing the trace along can only find the leakage, but it cannot find the complex relationship between the leakage site and the original buffer. For example, if two leakage sites leak the same information in the original buffer, those approaches cannot find out the two leakage sites are the same.

@@

Those methods usually follow the below steps. Suppose a program $P$ has $k$ as the input, we can run symbolic execution on the top the victim program. So temporary values can be represented as math formulas. After that, we need to build a cache or memory access model and model the side-channel leakage as a math constraint. Then we use SMT solvers to find if there are two different secret inputs that can lead to access different locations in the memory or the cache. If so, then the program is vulnerable to side-channel attacks. Contrary to the trace comparison, the method is quite precise. Moreover, it can model multiple leakages precisely as the conjunction of those formulas. However, after some initial investigations and experiments, we find such approach fails in practice due to the below reasons.

@@

According to Table~\ref{table:side_channel_detection_tool}, some methods may choose to analyze the source code or the intermediate languages. However, it still cannot solve the problem. First, many widely-used libraries (e.g., Intel MKL) do not open the source code. Second, some libraries use hand code assembly code to pursue the maximum performance. CacheAudit~\cite{182946} uses abstract domains to compute an
over approximation of cache-based side-channel information leakage upper bound.
However, it is difficult to judge the sensitive level of the side-channel leakage based on
the leakage provided by CacheAudit. CacheS~\cite{236338} improves on
CacheAudit with new abstract domains that only track
secret-related code. Like CacheAudit, CacheS cannot
indicate the sensitive level of side-channel vulnerabilities.
CaSym~\cite{Brotzman19Casym} introduces a static cache-aware symbolic
reasoning technique to cover multiple paths in a target program. Again, their
approaches cannot evaluate the sensitive level for each side-channel
vulnerability, and it only work on small code snippets.

The dynamic approach, usually consists of taint analysis and symbolic execution,
can perform a very precise analysis. CacheD~\cite{203878} takes a concrete execution trace and runs symbolic execution on the trace
to get the formula of each memory address. CacheD is
quite precise in avoiding false positives. However, CacheD is not able to detect secret-dependent control-flows. We adopted a similar approach to model the secret-dependent data accesses. \tool{} differs from CacheD in that we do not use traditional taint tracking or domain knowledge to cut the trace when identifying secret-dependent data access vulnerabilities. \tool{} works on machine instructions directly instead of intermediate representations. Moreover, \tool{} finds secret-dependent control-flows at the same time and gives a precise quantification of the leakage. DATA~\cite{217537} detects address-based side-channel vulnerabilities by comparing different execution traces under various test inputs. After collecting execution traces, DATA aligns them and finds the differences. It uses statistical hypothesis testing to find true leakages. However, both imperfect trace alignment and statistical testing result that DATA can produce false positives.
MicroWalk~\cite{Wichelmann:2018:MFF:3274694.3274741} uses
mutual information (MI) between sensitive input and execution state to detect side-channels.

\begin{table}
    \centering
    \caption{Due to the page limit, we only shows some representations of the vast side-channel attacks: Attacks, the shared hardware resources with attackers, the granularity of the attacker can observe, is there any published attacks on non-cryptography library and if the type of attack can exploit multiple leakage sites.}
    \label{table:side_channel_detection_tool}
    \resizebox{\columnwidth}{!}{%

Both hardware~\cite{Page2005PartitionedCA,
Wang:2007:NCD:1250662.1250723,Zhang:2015:HDL:2775054.2694372,Li:2014:SLH:2541940.2541947,
236344, 236334} and software~\cite{shih2017t,Coppens:2009:PMT:1607723.1608124,
brickell2006software,crane2015thwarting, 197207} side-channels mitigation techniques have
been proposed recently. Hardware countermeasures, including partitioning hardware resources~\cite{Page2005PartitionedCA}, randomizing cache
accesses~\cite{Wang:2007:NCD:1250662.1250723, 236344}, and designing new
architecture~\cite{tiwari2011crafting}, require changes to complex processors and are complex to adopt. On the contrary, software approaches are
usually easy to implement. Coppens et
al.~\cite{Coppens:2009:PMT:1607723.1608124} uses a compiler
to eliminate key-dependent control-flow transfers. Crane et
al.~\cite{crane2015thwarting} mitigated side-channels by randomizing software.
As for crypto libraries, the basic idea is to eliminate key-dependent
control-flow transfers and data accesses. Common approaches include
bit-slicing~\cite{konighofer2008fast,rebeiro2006bitslice} and unifying
control-flows~\cite{Coppens:2009:PMT:1607723.1608124}.

>>>>

Some other side-channel targets also include spell checking tools, and font libraries~\cite{xu2015controlled}. The attack to font libraries is essentially the same as the attack to the graphic library like GTK. By exploiting the differences of memory accesses when the program renders different characters, an attacker can recover parts of the original sensitive information. Other side-channel attacks target on the kernel of the operating system. One example is the to use the side-channel attacks to break the kernel address space randomization (KASLR).
Many exploits rely on the knowledge of the memory location of a certain kernel function. Since Linux 4.12, the kernel loads core kernel image and device drivers at random positions during the boot time. Jang et al.~\cite{jang2016breaking} rely on side-channels to reveal mapping status of each page. After that, they detect kernel modules with unique size signatures to break KASLR. The second example relies on the side-channel vulnerabilities~\cite{cao2019principled} inside kernels to infer the TCP sequence numbers, which can be used to hijack connections between the client and the server~\cite{cao2016off}.

\section{Detection and Mitigation}
While there are several existing work on side-channel leakage detections, we find it very hard to apply existing methods to identify controlled-channel attacks. According to Table~\ref{table:side_channel_detection_tool}, existing methods can be classified into two categories, tools based on the trace comparison and tools based on the abstraction.

\textbf{Trace comparison.} If a program has two different execution traces under two different sensitive inputs, then attacker can distinguish the sensitive input by observing the execution trace. Therefore, we can conclude the program is vulnerable to side-channel attacks. The method is similar to UNIX tool \textsf{diff}. Moreover, the approach does not need to model or abstract the program's semantics. In general, the approach is quite fast. On the negative side, comparing the trace along can find the leakage, but it cannot find the complex relationship between the leakage site and the original buffer. For example, if two leakage sites leak the same information in the original buffer, those approaches cannot find out the two leakage sites are the same.

@@

Those methods usually follow the below steps. Suppose a program $P$ has $k$ as the input, we can run symbolic execution on the top the victim program. So temporary values can be represented as math formulas. After that, we need to build a cache or memory access model and model the side-channel leakage as a math constraint. Then we use SMT solvers to find if there are two different secret inputs that can lead to access different locations in the memory or the cache. If so, then the program is vulnerable to side-channel attacks. Contrary to the trace comparison, the method is quite precise. Moreover, it can model multiple leakages precisely as the conjunction of those formulas. However, such approach has the following limitations.

@@

According to Table~\ref{table:side_channel_detection_tool}, some methods may choose to analyze the source code or the intermediate representations of the vulnerable software. However, it still cannot solve the problem. First, many widely-used libraries (e.g., Intel MKL) do not open the source code. Second, some libraries use hand code assembly code to pursue the maximum performance. CacheAudit~\cite{182946} uses abstract domains to compute an
over approximation of cache-based side-channel information leakage upper bound.
However, it is difficult to judge the sensitive level of the side-channel leakage based on
the leakage provided by CacheAudit. CacheS~\cite{236338} improves the approach from
CacheAudit with a new abstract model that only track
secret-related code. Like CacheAudit, CacheS cannot
indicate the sensitive level of side-channel vulnerabilities.
CaSym~\cite{Brotzman19Casym} introduces a static cache-aware symbolic
reasoning technique to cover multiple paths in a target program. Again, their
approaches cannot evaluate the sensitive level for each side-channel
vulnerability, and it only work on small code snippets.

The dynamic approach, usually consists of taint analysis and symbolic execution,
can perform a very precise analysis. CacheD~\cite{203878} takes a concrete execution trace and runs symbolic execution on the trace
to get the formula of each memory address. CacheD is
quite precise in avoiding false positives. However, CacheD is not able to detect secret-dependent control-flows. We adopted a similar approach to model the secret-dependent data accesses. \tool{} differs from CacheD in that we do not use traditional taint tracking or domain knowledge to cut the trace when identifying secret-dependent data access vulnerabilities. \tool{} works on machine instructions directly instead of intermediate representations. Moreover, \tool{} finds secret-dependent control-flows at the same time and gives a precise quantification of the leakage. DATA~\cite{217537} detects address-based side-channel vulnerabilities by comparing different execution traces under various test inputs. After collecting execution traces, DATA aligns them and finds the differences. It uses statistical hypothesis testing to find true leakages. However, both imperfect trace alignment and statistical testing result that DATA can produce false positives.
MicroWalk~\cite{Wichelmann:2018:MFF:3274694.3274741} uses mutual information (MI) between sensitive input and execution state to detect side-channels. 
\begin{adjustbox}{angle=90}

\begin{table*}
%\centering
\caption{Existing leakage detection tool only evaluate them on cryptography library. 1. Most recent work only evaluates their approaches on cryptography libraries. 2. All of them can not reason about the total effect of multiple leakages.}
\label{table:related_work}
\resizebox{2\columnwidth}{!}{%

\begin{tabular}{lllcclc}
\toprule
Tool & S/D & Method  & AVX/SIMD  & Multiple & Evaluation & Available \\ \midrule
CacheAudit~\cite{doychev2015cacheaudit} & Static  & Abstraction  & \xmark & \xmark & Crypto Algorithm  & \cmark \\ 
CacheD~\cite{wang2017cached} & Dynamic  & Symbolic Execution + Taint Analysis  & \xmark & \xmark & Libgcrypt, OpenSSL & \xmark \\
CachSym~\cite{brotzman2019casym} & Static & Symbolic Execution  & \xmark & \xmark & Crypto Snippet & \xmark \\
CacheS~\cite{wang2019identifying} & Static & Abstract Interpretation & \xmark & \xmark & Libgcrypt, OpenSSL, mbedTLS & \xmark \\
DATA~\cite{weiser2018data} & Dynamic & Trace Alignment + Comparison & \cmark & \xmark & OpenSSL, PyCrypto & \cmark \\
ctgrind~\cite{langley2010ctgrind} & Dynamic & Taint Analysis & \cmark & \xmark & Crypto Library & \cmark \\
Satcco~\cite{xiao2017stacco} & Dynamic & Trace Comparison & \cmark & \xmark & OpenSSL, GnuTLS, mbedTLS, WolfTLS, LibreSSL & \xmark \\
ANABLEPS~\cite{wang2019time} & Dynamic & Trace Comparison & \cmark & \xmark & Deep Learning, gsl, Hunspell, PNG, Freetype, QRcodegen, Genometools & \xmark \\
MicroWalk~\cite{wichelmann2018microwalk} & Dynamic & Trace Comparison & \cmark & \xmark & Intel IPP, Microsoft CNG & \cmark \\ 
\bottomrule
\end{tabular}
}
\end{table*}
\end{adjustbox}
Both hardware~\cite{Page2005PartitionedCA,
Wang:2007:NCD:1250662.1250723,Zhang:2015:HDL:2775054.2694372,Li:2014:SLH:2541940.2541947,
236344, 236334} and software~\cite{shih2017t,Coppens:2009:PMT:1607723.1608124,
brickell2006software,crane2015thwarting, 197207} side-channels mitigation techniques have
been proposed recently. Hardware countermeasures, including partitioning hardware resources~\cite{Page2005PartitionedCA}, randomizing cache
accesses~\cite{Wang:2007:NCD:1250662.1250723, 236344}, and designing new
architecture~\cite{tiwari2011crafting}, require changes to complex processors and are complex to adopt. On the contrary, software approaches are
usually easy to implement. Coppens et
al.~\cite{Coppens:2009:PMT:1607723.1608124} uses a compiler
to eliminate key-dependent control-flow transfers. Crane et
al.~\cite{crane2015thwarting} mitigated side-channels by randomizing software.
As for crypto libraries, the basic idea is to eliminate key-dependent
control-flow transfers and data accesses. Common approaches include
bit-slicing~\cite{konighofer2008fast,rebeiro2006bitslice} and unifying
control-flows~\cite{Coppens:2009:PMT:1607723.1608124}.
